Top-Down Graph-Based Neuron Reconstruction

### 2017-11-14 papers/cvpr2018/1_related_work.tex
paper: addressed HP comments

A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}. However these methods do not scale to terabyte datasets. More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u}.\hp{add more refs}

@@

Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Many methods build on top of these methods and train random-forest classifiers \hp{really?} to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}. \hp{are these agglomeration techniques based on watershed?}

@@

Some recent research builds on top of these region-based methods to correct errors in the segmentation~\cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based agglomerated segmentations for a true top-down reconstruction approach. This allows us to enforce domain-specific constraints using graph-based partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis,keuper2015efficient}. We use the method of X et al.\hp{add ref} to partition the extracted 3D graph into the final neuron reconstruction.

>>>>

A large amount of connectomics research considers the problem of extracting segmentation information at the pixel (i.e., voxel) level from the raw EM images. Some early techniques apply computationally expensive graph partitioning algorithms with a single node per pixel~\cite{andres2012globally}. However these methods do not scale to terabyte datasets. More recent methods train classifiers to predict membrane probabilities per image slice either using 2D~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation} or 3D CNNs~\cite{lee2015recursive,ronneberger2015u,turaga2010convolutional}.

@@

Several pixel-based approaches generate probabilities that neighboring pixels belong to the same neuron.
Often a watershed algorithm will cluster pixels into small super-pixels~\cite{zlateski2015image}. 
Many methods build on top of these strategies and train random-forest classifiers to produce region-based (i.e., super-pixel) segmentations~\cite{seymour2016rhoananet,nunez2014graph,10.1371/journal.pone.0125825,parag2017anisotropic,zlateski2015image}.

@@

Some recent research builds on top of these region-based methods to correct errors in the segmentation~\cite{rolnick2017morphological,error_correction_using_CNN,haehn2017guided}.
However, to our knowledge, our method is the first to extract a 3D graph from pixel-based agglomerated segmentations for a true top-down reconstruction approach. This allows us to enforce domain-specific constraints using graph-based partitioning algorithms. Many segmentation and clustering algorithms use graph partitioning techniques~\cite{andres2012globally} or normalized cuts for traditional image segmentation~\cite{kappes2016higher,shi2000normalized,tatiraju2008image}.
Even though graph partitioning is an NP-Hard problem~\cite{demaine2006correlation} there are several useful multicut heuristics that provide good approximations with reasonable computational costs~\cite{horvnakova2017analysis}. We use the method of Keuper et al. to partition the extracted 3D graph into the final neuron reconstruction~\cite{keuper2015efficient}.

### 2017-11-14 papers/cvpr2018/2_method.tex
paper: addressed HP comments

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors (CITE)\hp{add}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments. We generate a skeleton for every segment based on the intuition that a skeleton represents a simplified representation of the overall shape of the neuron. We generate a simplified 3D graph from the skeletons by locating merge candidates and producing corresponding edges.\hp{check prior sentence} We train a CNN to  generate the edge weights by learning a merge function from ground truth data. A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. We will now discuss the three major components to our framework (skeletonization, CNN, and graph-partition) in more detail. \hp{stopped here}

>>>>

There are two types of errors that can occur in connectomics segmentation.
The first, called a split error, occurs when there are two segments that should have been merged. The second, called a merge error, happens when one segment should be split into two. Generally, it is much more difficult to correct merge errors than to correct split errors~\cite{parag2015properties}, which is why most reconstruction approaches are tuned towards over-segmentation with many more split than merge errors. Our method takes as input over-segmentations of EM image volumes generated by state-of-the-art connectomics reconstruction pieplines (Sec.~\ref{sec:neuroproof}). Our goal is to identify locations of split errors and merge the corresponding segments automatically.

From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. The nodes correspond to label segments from the segmentation with edges between segments considered for merging. Ideally, our graph has edges corresponding to all of the segments which were erroneously split with few edges between correctly split segments. 
We generate a skeleton for every segment based on the intuition that a skeleton represents a simplified representation of the overall shape of the neuron. 
From this skeleton we quickly identify potential merge locations and produce the corresponding edges for the graph. 
We train a CNN to  generate the edge weights by learning a merge function from ground truth data. A multicut heuristic generates a partition on the graph where nodes in the same partition are assigned the same output label. We will now discuss the three major components to our framework (skeletonization, CNN, and graph-partition) in more detail. \hp{stopped here}
